Array Programming with NumPy

### 2020-06-02 methods.tex
Provide response to referee comment on random

@@

NumPy's linear algebra library provides an interface to established
linear algebra methods. These include solving linear systems of equations
and computing various matrix properties, such as the determinant,
the norm, the inverse, and the pseudo-inverse.
As well as computing the Cholesky, eigenvalue, and singular value decompositions
of a matrix and further functions.
For best performance and reliability the algorithms are provided by leveraging
an external implemention of the LAPACK interface \cite{LAPACK}.
LAPACK itself was first released in 1992 and is based on the EISPACK and LINPACK
open-source libraries. It is part of Netlib, a repository of
mathematical software, papers and databases and has a long history of open,
community-wide development. \cite{dongarra1990lapack,dongarra2008netlib}

@@

Bit generators are simple classes that manage the state of an underlying
pseudorandom number generator. NumPy ships with four bit generators. The default
bit generator is a 64-bit implementation of the Permuted Congruential Generator
\cite{pcg64} (\texttt{PCG64}). The three other bit generators are a 64-bit version
of the Philox generator\cite{random123} (\texttt{Philox}), Chris Doty-Humphrey's
Small Fast Chaotic generator\cite{practrand} (\texttt{SFC64}), and the 32-bit
Mersenne Twister\cite{mt19937} (\texttt{MT19937}) which has been used in older
versions of NumPy.\footnote{The
\href{https://github.com/bashtage/randomgen}{randomgen project} supplies a wide
range of alternative bit generators such as a cryptographic counter-based
generators (\texttt{AESCtr}) and generators that expose hardware random number
generators (\texttt{RDRAND})\cite{randomgen}.} Bit generators provide
functions, exposed both in Python and C, for generating random integer
and floating point numbers.

The \texttt{Generator} consumes one of the bit generators and produces variates
from complicated distributions. Many improved methods for generating random
variates from common distributions were implemented, including the Ziggurat
method for normal, exponential and gamma variates\cite{ziggurat}, and Lemire's
method for bounded random integer generation\cite{lemire}. The \texttt{Generator}
is more similar to the legacy \texttt{RandomState}, and its API is substantially
the same. The key differences all relate to state management, which has been
delegated to the bit generator. The \texttt{Generator} does not make the same
stream guarantee as the \texttt{RandomState} object, and so variates may differ
across versions as improved generation algorithms are
introduced.\footnote{Despite the removal of the compatibility guarantee, simple
reproducibility across versions is encouraged, and minor changes that do not
produce meaningful performance gains or fix underlying bug are not generally
adopted.}

>>>>

NumPy's linear algebra library provides an interface to established
linear algebra methods. These include solving linear systems of equations
and computing various matrix properties, such as the determinant,
the norm, the inverse, and the pseudo-inverse.
As well as computing the Cholesky, eigenvalue, and singular value decompositions
of a matrix and further functions.
For best performance and reliability the algorithms are provided by leveraging
an external implemention of the LAPACK interface \cite{LAPACK}.
LAPACK itself was first released in 1992 and is based on the EISPACK and LINPACK
open-source libraries. It is part of Netlib, a repository of
mathematical software, papers and databases and has a long history of open,
community-wide development \cite{dongarra1990lapack,dongarra2008netlib}.

@@

@@

Bit generators are simple classes that manage the state of an underlying
pseudorandom number generator. NumPy ships with four bit generators. The default
bit generator is a 64-bit implementation of the Permuted Congruential Generator
\cite{pcg64} (\texttt{PCG64}). The three other bit generators are a 64-bit version
of the Philox generator \cite{random123} (\texttt{Philox}), Chris Doty-Humphrey's
Small Fast Chaotic generator \cite{practrand} (\texttt{SFC64}), and the 32-bit
Mersenne Twister \cite{mt19937} (\texttt{MT19937}) which has been used in older
versions of NumPy.\footnote{The
\href{https://github.com/bashtage/randomgen}{randomgen project} supplies a wide
range of alternative bit generators such as a cryptographic counter-based
generators (\texttt{AESCtr}) and generators that expose hardware random number
generators (\texttt{RDRAND}) \cite{randomgen}.} Bit generators provide
functions, exposed both in Python and C, for generating random integer
and floating point numbers. The three new bit generators were chosen for their
combination of statistical soundness and performance. The PCG family of generators
have been widely tested using state-of-the-art statistical tests and found to
perform well (\cite{lemire_blog}). All three of the new generators were tested
using the PractRand test suite (\cite{practrand}) with four TB of random values.
Each was tested using a single generator and using a composite generator assembled
from multiple copies of the same bit generator, each seeded from a shared
\texttt{SeedSequence}.

The \texttt{Generator} consumes one of the bit generators and produces variates
from complicated distributions. Many improved methods for generating random
variates from common distributions were implemented, including the Ziggurat
method for normal, exponential and gamma variates \cite{ziggurat}, and Lemire's
method for bounded random integer generation \cite{lemire}. The \texttt{Generator}
is more similar to the legacy \texttt{RandomState}, and its API is substantially
the same. The key differences all relate to state management, which has been
delegated to the bit generator. The \texttt{Generator} does not make the same
stream guarantee as the \texttt{RandomState} object, and so variates may differ
across versions as improved generation algorithms are
introduced.\footnote{Despite the removal of the compatibility guarantee, simple
reproducibility across versions is encouraged, and minor changes that do not
produce meaningful performance gains or fix underlying bug are not generally
adopted.}
